Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-07 1-Main.tex
Change title
Updates from Overleaf

%\documentclass[preprint]{acmart}
\documentclass[american]{emisa}

@@

\newcommand{\noteSM}[1]{\todo[color=red!40, author=\textbf{Salvador}, inline, caption={}]{#1}}
\newcommand{\noteJC}[1]{\todo[color=pink!40, author=\textbf{JC}, inline, caption={}]{#1}}
\newcommand{\noteSylvain}[1]{\todo[color=green!40, author=\textbf{Sylvain}, inline, caption={}]{#1}}
\newcommand{\noteAntoine}[1]{\todo[color=yellow!40, author=\textbf{Antoine}, inline, caption={}]{#1}}
\newcommand{\noteFabien}[1]{\todo[color=orange!40, author=\textbf{Fabiem}, inline, caption={}]{#1}}

@@

%\acmPrice{15.00}
%\acmDOI{10.1145/1122445.1122456}
%\acmISBN{978-1-4503-9999-9/18/06}

\begin{document}
\begin{article}{
\title{\mpc: the FML solution}

@@

\abstract{\input{2-Abstract}}
\keywords{Multilevel Modeling Challenge, Federation Modeling Language, OpenFlexo}
\bibliography{}
}
%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.

@@

\noteSM{test}
\noteJC{test}
\noteSylvain{Test}
\noteAntoine{Test}
\noteFabien{test}

@@

%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
%\bibliographystyle{ACM-Reference-Format}
\bibliography{biblio}

% à utiliser d'après le style (avec biber), voir comment ça fonctionne sous overleaf, sinon CLI et tant pis/mieux
%\printbibliography

\end{article}
\end{document}
\endinput
%%

>>>>

\documentclass[american]{emisa}

@@

\newcommand{\noteSM}[1]{\todo[color=red!40, author=\textbf{Salvador}, inline, caption={}]{#1}}
\newcommand{\noteJC}[1]{\todo[color=pink!40, author=\textbf{JC}, inline, caption={}]{#1}}
\newcommand{\noteSylvain}[1]{\todo[color=green!40, author=\textbf{Sylvain}, inline, caption={}]{#1}}
\newcommand{\noteAntoine}[1]{\todo[color=yellow!40, author=\textbf{Antoine}, inline, caption={}]{#1}}
\newcommand{\noteFabien}[1]{\todo[color=orange!40, author=\textbf{Fabien}, inline, caption={}]{#1}}
\newcommand{\noteJoel}[1]{\todo[color=blue!20, author=\textbf{Joel}, inline, caption={}]{#1}}

@@

\begin{document}
\begin{article}{
%\title{\mpc: the FML solution}
\title{Multi-level modelling with Openflexo/FML - A contribution to the \mpc}

@@

\abstract{\input{2-Abstract}}
\keywords{Multilevel Modeling Challenge, Federation Modeling Language, OpenFlexo}
\bibliography{biblio.bib}

}
%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.

@@

\noteSM{test}
\noteJC{test}
\noteSylvain{test}
\noteAntoine{test}
\noteFabien{test}
\noteJoel{test}

@@

\printbibliography

\end{article}
\end{document}
%%

### 2021-05-07 6-ModelPresentation.tex
Updates from Overleaf

>>>>

We will illustrate the base metamodel presented in this section with XSure insurance domain use case, whose a partial description was provided in the challenge description. Note that the capture of the requirements P1 to P19 in the context of XSure insurance domain are straightforward implementable while instantiating base metamodel presented in figure \ref{fig:BaseMetamodel}.
